---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tibble)
```

# cjr

<!-- badges: start -->
<!-- badges: end -->

cjr (CEFAGE-UE Journal Ranking) is an R data package that provides
[CEFAGE](http://www.cefage.uevora.pt)’s journal ranking. CEFAGE-UE stands for
*Center for Advanced Studies in Management and Economics*, a research centre
from the University of Évora, Portugal.

This package contains four datasets:

- `journals`: CEFAGE-UE journals' ranking
- `rates`: CEFAGE-UE journals' rate categories
- `scientific_fields`: Journals' scientific fields
- `publishing_presses`: Journals' publishing presses

## Installation

You can install cjr with:

``` r
# Install the development version from GitHub
devtools::install_github("ramiromagno/cjr")
```

## Data source

The datasets here provided are for the 4th edition (2016-2019): http://www.cefage.uevora.pt/en/scientific_resources/ranking_de_revistas_cientificas.

## Usage

### CEFAGE-UE ranking of journals

The main dataset, i.e., `journals`, contains the ranking of 903 journals in the field of Economics, Management, and other social sciences, for the period of 2016 thru 2019:

```{r}
library(cjr)
journals
```

Sort journals by rate within scientific domain:

```{r message=FALSE}
library(dplyr)
arrange(journals, scientific_field_abbr, desc(rate))
```

### Rates

The rates defined by CEFAGE-UE to rank journals are listed in `rates`:

```{r}
rates
```

### Journals’ scientific fields

Journals' scientific domains abbreviations used in `journals` are provided in `scientific_fields`:

```{r}
scientific_fields
```

### Journals’ publishing presses

Journals' publishing presses abbreviations used in `journals` are provided in `publishing_presses`:

```{r}
publishing_presses
```

